Abstraction and Invariance for Algebraically Indexed Types

### 2012-10-23 paper/paper.tex
Revamped section on general non-definability results
Add Kenneth to the list of acknowledgements.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{section-introduction.tex}
\input{geometry-twocolumn.tex}
\input{section-general-framework.tex}
\input{section-instantiations.tex}
\input{section-monoid.tex}
\input{section-info-flow.tex}
%\input{section-singleton.tex}
\input{section-metric.tex}
\input{section-discussion.tex}

@@

\section*{Acknowledgements}
The authors would like to thank Nick Benton, John Reppy and Martin Will for 
illuminating discussions on geometry and types.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{section-introduction.tex}
\input{geometry-twocolumn.tex}
\input{section-general-framework.tex}
\input{section-instantiations.tex}
\input{section-general-nondef.tex}
\input{section-info-flow.tex}
%\input{section-singleton.tex}
\input{section-metric.tex}
\input{section-discussion.tex}

@@

\section*{Acknowledgements}
The authors would like to thank Nick Benton, Kenneth MacKenzie, John
Reppy and Martin Will for illuminating discussions on geometry and
types.
